\section*{Cleric}%%%%%%%%%%%%%%%CLERIC
\addcontentsline{toc}{subsection}{Cleric}
\begin{multicols}{3}
\begin{mercClassInfo}
\textbf{Casting Attribute:} Spirit\\
\textbf{Armor:} All\\
\textbf{Weapons:} Weapons with Blunt Property
\end{mercClassInfo}
\end{multicols}
\subsubsection*{Level Progression}
\begin{table}[H]

\begin{center}

\Large
\rowcolors{2}{gray!30}{greg}
\centering
\begin{tabularx}{\textwidth}{>{\centering\arraybackslash\hsize=.2\hsize}X 
>{\centering\arraybackslash\hsize=.2\hsize}X
>{\centering\arraybackslash\hsize=.3\hsize}X
>{\centering\arraybackslash\hsize=.2\hsize}X
>{\centering\arraybackslash\hsize=.55\hsize}X
>{\centering\arraybackslash\hsize=.55\hsize}X}



\hiderowcolors
 \textbf{
Level}& \textbf{XP} &\textbf{Hit Dice} &\textbf{Divinity} &  \textbf{Max Miracle Power} & \textbf {Attack Bonus}\\
\hline
\hline
%\bottomrule
\showrowcolors
\centering
1 &0&  1d6  & 1 & 1 & 0\\

2 &2000&  2d6 & 2 & 1 & 1 \\

3 &4000& 3d6 & 3 & 2 & 1 \\

4 &8000& 4d6 & 4 & 2 & 2 \\

5 &16000& 5d6 & 5 & 3 & 2 \\

6 &32000& 6d6 &6 & 3 & 3 \\

7 &64000& 7d6 & 7 & 4 & 3 \\

\end{tabularx}
\end{center}
\label{table:Cleric}
\end{table}

\begin{multicols}{2}%%%Cleric data

\begin{mercHeading}
Divine Spellcasting
\end{mercHeading}

See  \textbf{pg \pageref{section:GenMagicRules} Magic} for general spellcasting rules. \\
\textbf{Miracles Known:} A first-level Cleric knows a number of miracles equal to \textbf{Spirit} (Min 1.) This number is split between 0th level miracles (cantrips) and 1st level miracles. When a magic user gains a level, they learn an additional miracle of a level less than or equal to the max miracle power of the table. \vspace{2pt}\\ 
\textbf{Miracle Scrolls:}
A Cleric is able to cast any Miracle scroll (For every level above max miracle power adds -1 to the attribute roll). Additionally, a Cleric can learn a miracle from a scroll after spending 1 day per miracle power in prayer.

\begin{mercHeading}
Turn Undead
\end{mercHeading}
A Cleric has a special ability with their holy symbol that can repel or destroy Undead creatures. The cleric makes a \textbf{Spirit} attribute roll that turns Undead up to Cleric Level HD and destroys half Cleric Level HD on a success. On a partial, turns half Cleric Level HD, and on a failure does nothing. \\


\end{multicols}
